---
title: "What Covid-19 is like in Bahrain?"
description: |
  Bahrain, a tiny Middle East country, has one of the highest vaccine coverage rate around the world!
author:
  - name: Janice Hsin Hsu
    url: https://example.com/norajones
date: 08-30-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(coronavirus)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(grid)
library(leaflet)
library(lubridate)
library(kableExtra)
```


```{r}
data("coronavirus")
bah <- subset(coronavirus, country == 'Bahrain') %>%
   mutate(date = ymd(date)) %>% 
  mutate_at(vars(date), funs(year, month, day))
```

## My first experiences in Bahrain

" Hey are you okay? Your face looks dreadfully pale."

" Yea nah I am not coping well with the ramadan."

" Here, take one of these, you are gonna feel much better."

Since then, I cannot forget the flavour and and sweetness of the dates nut that one of the Bahrainian gave me.

Bahrain was only a really unfamiliar country name for me until I received a job opportunity as a project manager in 2018. It has been three years since I went to Bahrain, but I still remember the heat, the desert and the hospitality that Bahrainians has offered me. I didn't get to spend a lot of time traveling around, especially because it was the fasting season when I went that I didn't even have the chance to really enjoy the food there. However, it was one of the special places that I have ever been.


```{r covid_situation_in_Bahrain}
g1 <- coronavirus %>%
  ggplot(aes(x = date, y = cases))+
  geom_col(col = "steelblue")+
ggtitle("World situation")
g2 <- bah %>%
ggplot(aes(x = date, y = cases))+
  geom_col(col = "steelblue")+
  ggtitle("Bahrain")

grid.arrange(g1, g2, ncol =2)
```



```{r table1}
bah %>%
  group_by(year, month) %>%
  summarise(`total case` = sum(cases)) %>%
   knitr::kable(
  caption = "Cases in each month") %>%
  kable_styling(c("hover", "striped"))
```






Learn more about using Distill at <https://rstudio.github.io/distill>.


